PhD Thesis

### 2016-06-22 pldi14/fig-primitives.tex
Integrate PLDI14 paper

\lstinputlisting[language=scala,
firstline=10,
escapechar=|,
literate=
{=>}{$\Rightarrow\,$}2
{>=}{$\ge\;$}2
{<-}{$\leftarrow\;$}2
{!=}{$\ne\;$}2
{Abelian-group-based}{\text{Abelian-group-based }}1
{<}{$<$}2
{bag1}{{bag$_1$}}4
{bag2}{{bag$_2$}}4
{value1}{{value$_1$}}6
{value2}{{value$_2$}}6
{dict1}{{dict$_1$}}5
{dict2}{{dict$_2$}}5
{v1}{{v$_1$}}2
{v2}{{v$_2$}}2
{???}{$\ldots$}3
]{mapReduce.scala}
\caption{A Scala implementation of primitives for bags and maps.
In the code, we call $\boxplus$, $\boxminus$ and $e$ respectively \emph{merge}, \emph{inverse}, and \emph{zero}.
We also omit the relatively standard primitives.\pg{Can we now move this code to an appendix, since we explain so much in text?}}
\label{fig:primitives}
\end{figure}

>>>>

\lstinputlisting[language=scala,
firstline=10,
escapechar=|,
literate=
{=>}{$\Rightarrow\,$}2
{>=}{$\ge\;$}2
{<-}{$\leftarrow\;$}2
{!=}{$\ne\;$}2
{Abelian-group-based}{\text{Abelian-group-based }}1
{<}{$<$}2
{bag1}{{bag$_1$}}4
{bag2}{{bag$_2$}}4
{value1}{{value$_1$}}6
{value2}{{value$_2$}}6
{dict1}{{dict$_1$}}5
{dict2}{{dict$_2$}}5
{v1}{{v$_1$}}2
{v2}{{v$_2$}}2
{???}{$\ldots$}3
]{pldi14/mapReduce.scala}
\caption{A Scala implementation of primitives for bags and maps.
In the code, we call $\boxplus$, $\boxminus$ and $e$ respectively \emph{merge}, \emph{inverse}, and \emph{zero}.
We also omit the relatively standard primitives.\pg{Can we now move this code to an appendix, since we explain so much in text?}}
\label{fig:primitives}
\end{figure}
